\pkg{partykit}: A Modular Toolkit for Recursive Partytioning in \proglang{R}

### 2014-10-22 pkg/partykit/inst/mloss/letter_mloss3.tex
added Strobl ref
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@629 255f4249-2263-4417-b1ea-8498779e27a7

Referee 3 criticised the limited breath of our contribution and suggested to
copy the \texttt{cforest} function from package \emph{party} to package
\emph{partykit}, iterating an argument by Referee 2 from the previous
round. In the rebuttal letter, we explain the reason why it is currently not
helpful to move this function from one CRAN package to another one. In
addition, we took the liberty to discuss why we think that \emph{partykit}
is actually much more general than \emph{party} and, if one adopts a certain
point of view, also more general than most of the established machine
learning toolboxes. Since no changes in the manuscript were requested, we
did not touch the four page description.

>>>>

Reviewer 3 criticises the limited breath of our contribution and suggests to
copy the \texttt{cforest} function from package \emph{party} to package
\emph{partykit}, iterating an argument by Reviewer 2 from the previous
round. In the rebuttal letter, we explain the reason why it is currently not
helpful to move this function from one CRAN package to another one. In
addition, we took the liberty to discuss why we think that \emph{partykit}
is actually much more general than \emph{party} and, if one adopts a certain
point of view, also more general than most of the established machine
learning toolboxes. Since no changes in the manuscript were requested, we
did not touch the four page description.
